---
title: "groupassigment-1"
output: html_notebook
---
Assigment Submission by 
1) Rohith Varier.  PGID : 11915064 EmailId : Rohith_Varier_cba2020s@isb.edu
2) Parul Gaba      PGID : 11915008 EmailId : Parul_Gaba_cba2020s@isb.edu
3) Niraj Kulkarni. PGID : 11915030 EmailId : Niraj_Kulkarni_cba2020s@isb.edu

References links referred for understanding:
https://www.datacamp.com/community/tutorials/linear-regression-R
https://solvemprobler.com/blog/2015/12/19/calculating-stocks-beta-using-r/


```{r, setup}
suppressPackageStartupMessages({
library(dplyr)
library(ggplot2)
library(magrittr)
})
```

Let us Calculate Returns by assuming that 1 share was bought 60 months ago i,e the first value in the data. 

Calculating simple returns.
We have taken 2 NIFTY 50 shares wiz TATA MOTORS and SBI.
Share1 = Tata Motors  Share2 = SBI 
```{r}
share1<-read.csv("TATAMOTORS.NS.csv",stringsAsFactors = FALSE , header = TRUE)
share1<-share1[!(share1$Adj.Close=='null' | is.na(share1$Adj.Close)) ,] #removing null
maxDate1<-share1 %>% head(1) #%>% arrange(share1$Date) 
minDate1<-share1 %>% tail(1) #%>% arrange(share1$Date) 
valShare1_1<-as.numeric(as.character(maxDate1$Adj.Close))
valShare1_2<-as.numeric(as.character(minDate1$Adj.Close))

share1_ret<-(valShare1_1/valShare1_2 - 1)*100
share1_ret 
```
Simple Return on Share1 Tata motors is : 140.1559
```{r}
plot(x=share1$Adj.Close,ylab = 'Adjusted Close',type='line',col='blue',main = 'TataMotors Monthly Closing')
```


```{r}
#SHARE2
share2<-read.csv("SBIN.NS.csv",stringsAsFactors = FALSE , header = TRUE)
share2<-share2[!(share2$Adj.Close=='null' | is.na(share2$Adj.Close)) ,] #removing null
maxDate2<-share2 %>% head(1) 
minDate2<-share2 %>% tail(1)
valShare2_1<-as.numeric(as.character(maxDate2$Adj.Close))
valShare2_2<-as.numeric(as.character(minDate2$Adj.Close))
share2_ret<-(valShare2_1/valShare2_2 - 1)*100
share2_ret  
```
Simple Return on Share1 SBI is : -18.71877
```{r}
plot(x=share2$Adj.Close,ylab = 'Adjusted Close',type = 'line',col='blue',main = 'SBI Monthly Closing')
```

```{r}
#NIFTY
nifty<-read.csv("Nifty50-NSEI.csv",stringsAsFactors = FALSE , header = TRUE)
nifty<-nifty[!(nifty$Adj.Close=='null' | is.na(nifty$Adj.Close)) ,] #removing null
maxDateN<-nifty %>% arrange(nifty$Date) %>% head(1) 
minDateN<-nifty %>% arrange(nifty$Date) %>% tail(1)
valNifty_1<-as.numeric(as.character(maxDateN$Adj.Close))
valNifty_2<-as.numeric(as.character(minDateN$Adj.Close))
nifty_ret<-(valNifty_1/valNifty_2 - 1)*100

nifty_ret   #49.87026
```
Simple Return on index Nifty is : -33.27562
```{r}
plot(x=nifty$Adj.Close,ylab = 'Adjusted Close',type = 'line',col='blue',main = 'Nifty Monthly Closing')
```

Let us now calculate Linear Regression of 2 shares against NIFTY 50 index. For predicting the value we are considering the nifty value i.e x variable as mean of nifty index.
```{r}
####### Linear Regression ######
regression_data<-data.frame("share1_close" = as.numeric(as.character(share1$Adj.Close)) ,
                            "share2_close" = as.numeric(as.character(share2$Adj.Close)),
                            "nifty_close"  = as.numeric(as.character(nifty$Adj.Close)))
#for share1
lmret1<-lm(regression_data$share1_close~regression_data$nifty_close,data = regression_data)
res<-summary(lmret1)
res
##from the summary
intercept1 <- res$coefficients[1,1] #945.873412
nifty_reg1 <- res$coefficients[2,1] #-0.059658
nifty_mean <- mean(as.numeric(as.character(nifty$Adj.Close)))
#share=a+nifty*b
#share1=Intercept + nifty * regression_data$nifty_close
#if nifty mean is used i,e 9299.774 then our regression model for tata share share1 will be 
share1_reg<- intercept1 + (nifty_reg1 *  nifty_mean)
share1_reg   #391.0659
```

```{r}
plot(regression_data$share1_close~regression_data$nifty_close, pch = 16, col = "blue") #plotting regression values
abline(lmret1) #regression line
```
Linear Regression model has predicted that Tata motors value will be = 391.0659 by taking Tata motors on left side and nifty index on right.
```{r}
#for share2
lmret2<-lm(regression_data$share2_close~regression_data$nifty_close,data = regression_data)
res2<-summary(lmret2)
res2
##from the summary
intercept2 <- res2$coefficients[1,1] #75.054194
nifty_reg2 <- res2$coefficients[2,1] #0.020348
nifty_mean <- mean(as.numeric(as.character(nifty$Adj.Close)))
#share=a+nifty*b
#share1=Intercept + nifty * regression_data$nifty_close
#if nifty mean is used i,e 9299.774 then our regression model for tata share share1 will be 

share2_reg<- intercept2 + (nifty_reg2 *  nifty_mean)
share2_reg
```

```{r}
plot(regression_data$share2_close~regression_data$nifty_close, pch = 16, col = "blue") #plotting regression values
abline(lmret2) #Add a regression line

```
Linear Regression model has predicted that SBI value will be = 264.2886 by taking SBI on left side and nifty index on right.

Let us now calculate the Beta on returns of the stock.
```{r}
######## Beta Calculation #########
share1Prices<-as.numeric(regression_data$share1_close)
share2Prices<-as.numeric(regression_data$share2_close)
niftyPrices<-as.numeric(regression_data$nifty_close)

stock1_returns<-((share1Prices[2:length(share1Prices)] - share1Prices[1:length(share1Prices)-1] )/share1Prices[1:length(share1Prices)-1])*100
stock2_returns<-((share2Prices[2:length(share2Prices)] - share2Prices[1:length(share2Prices)-1] )/share2Prices[1:length(share2Prices)-1])*100
index_returns<-((niftyPrices[2:length(niftyPrices)] - niftyPrices[1:length(niftyPrices)-1] )/niftyPrices[1:length(niftyPrices)-1])*100

regOnReturns_share1 <- lm(stock1_returns ~ index_returns)
summary_share1 <- summary(regOnReturns_share1)

beta_val_share1 <- summary_share1$coefficients[2,1]
print(beta_val_share1)

regOnReturns_share2 <- lm(stock2_returns ~ index_returns)
summary_share2 <- summary(regOnReturns_share2)

beta_val_share2 <- summary_share2$coefficients[2,1]
print(beta_val_share2)
```
Beta Value of Share1 ie TATA MOTORS stock is 1.712694
Beta Value of Share1 ie SBI stock is 1.575992
